\textbf{Manual Coding Guidelines\\[0.15cm] for Automation Patents}

### 2015-09-02 manual_coding_guidelines/manual_coding_guidelines.tex
Typo and formatting

\begin{frame}\frametitle{When you're done}
	\begin{itemize}	
		\item Please make sure your file is formatted the following way:\\[0.1cm]
\texttt{manclass\textunderscore <FirstnameLastname>\textunderscore <year>-<month>-<day>.xlsx}\\[0.3cm]
		for example, for Lukas on the 11\textsuperscript{th} of May 2015 that would be:\\[0.1cm]
\texttt{manclass\textunderscore LukasPuettmann\textunderscore 2015-05-11.xlsx}\\[0.3cm]
		\item and then send it back to us in an email to \href{mailto:katja.mann@uni-bonn.de}{\texttt{katja.mann@uni-bonn.de}} or \href{mailto:lukas.puettmann@uni-bonn.de}{\texttt{lukas.puettmann@uni-bonn.de}}		
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Some empirical probabilities}
So far, the different fields were marked the following frequencies:
	\begin{itemize}	
		\item Automation patent: 27\%, of those:
		\begin{itemize}
			\item manual: 42\%
			\item cognitive: 46\%
			\item both: 12\%
			\item neither: 0\% (none so far)
		\end{itemize}
	\end{itemize}
\end{frame}

>>>>

\begin{frame}\frametitle{When you're done}
	\begin{itemize}	
		\item Please make sure your file is formatted the following way:\\[0.1cm]
\texttt{manclass\textunderscore <FirstnameLastname>\textunderscore <year>-<month>-<day>.xlsx}\\[0.3cm]
		for example, for Lukas on the 11\textsuperscript{th} of May 2015 that would be:\\[0.1cm]
\texttt{manclass\textunderscore LukasPuettmann\textunderscore 2015-05-11.xlsx}\\[0.3cm]
		\item and then send it back to us in an email to \href{mailto:katja.mann@uni-bonn.de}{\textcolor{myred}{\texttt{katja.mann@uni-bonn.de}}} or \href{mailto:lukas.puettmann@uni-bonn.de}{\textcolor{myred}{\texttt{lukas.puettmann@uni-bonn.de}}}		
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Some empirical probabilities}
So far, the different fields were marked with the following frequencies:
	\begin{itemize}	
		\item Automation patent: 27\%, of those:
		\begin{itemize}
			\item manual: 42\%
			\item cognitive: 46\%
			\item both: 12\%
			\item neither: 0\% (none so far)
		\end{itemize}
	\end{itemize}
\end{frame}
